Dismal Code: Studying the Evolution of Security Bugs

### 2013-02-06 docs/msr.tex
arch figure
playing with the authors

@@

\author{
\IEEEauthorblockN{Dimitris Mitropoulos}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: dimitro@aueb.gr}\\
\and
\IEEEauthorblockN{Vassilios Karakoidas}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: bkarak@aueb.gr}\\
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{Department of Software and Computer Technology\\
Delft University of Technology\\
Email: G.Gousios@tudelft.nl}\\
\and
\IEEEauthorblockN{Panos Louridas}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: louridas@aueb.gr}\\
\and
\IEEEauthorblockN{Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: dds@aueb.gr}}

>>>>

\author{
\IEEEauthorblockN{Dimitris Mitropoulos, Vassilios Karakoidas, Georgios Gousios, Panagiotis Louridas, Diomidis Spinellis}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Management Science and Technology\\
Athens University of Economics and Business\\
\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\ \\
\IEEEauthorblockA{TODO: Add Affiliation here\\
Delft University of Technology\\
Email: G.Gousios@tudelft.nl}
}

@@
